NFC and burnout in teachers - A replication and extension study

### 2022-07-20 Manuscript/Revision_Letter.Rmd
started arguing the teacher-boredom case

>>>>

Thank you for addressing this.
We do not consider "being busy" to be the same as "not being bored", because while an employee might have a high workload, the tasks in question might not be interesting or stimulating at all.
In the case of teachers it might be grading essays on a topic they have read about many times, or staying at work until the late evening for parent-teacher conferences.
We looked into the literature on boredom in teachers and found that boredom was one of the main reasons for leaving the job (Tye & O'Brien 2022, https://doi.org/10.1177/003172170208400108), teachers were just as bored during class as their students (Tam et al. 2019, https://doi.org/10.1111/bjep.12309), and teachers have a strong feeling of mission and responsibility but lack the opportunities to implement these priorities (Tuisk 2007, https://doi.org/10.2478/v10099-009-0011-8).
